\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2017-05-24 latex_corrected/UMEM_CoSim.tex
changes addressing Review 2, question (2) a) through g) (g was omitted)

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
\usepackage{lmodern}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{lineno}
\usepackage{tikz}
\RequirePackage{fix-cm}

@@

@@

\subsection{EnergyPlus co-simulation results}
After calibration, a comparison of co-simulation and solo EnergyPlus
simulations is made. For cooling, a discrepancy can be seen between co-
simulation and solo EnergyPlus. Co-simulation decreases the predicted cooling energy by 15.5\%, as seen in Figure
\ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating}
illustrates the difference in predicted heating energy consumption across the
test year. A consistent offset exists across the time frame of days in
January, the peak of the heating season. A more varied discrepancy across the
heating months is noticed resulting an overall increase of heating prediction
of 6.5\% due to co-simulation. The exchange of long wave radiation for this
particular site is substantial due to the proximity of surrounding buildings.
These performance differences due to co-simulation are compared to a
theoretical single-zone case study in which there was a 15-30\% increase in
heating energy and a 4-11\% decrease in cooling energy \citep{Miller:2015vk}.
The results from this case study are less extreme on the heating side and more
on the cooling side than the theoretical case study.

>>>>

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
\usepackage{lmodern}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{lineno}
\RequirePackage{fix-cm}

@@

The number of timesteps per hour for both CitySim and EnergyPlus is set to one per hour. 
The frequency of data exchanges is set to once per timestep. No data averaging over time 
is performed. Data exported from one simulation engine overwrites the corresponding data
in the other simulation engine at each timestep. Each simulation is performed for a whole 
year.

@@

\subsection{EnergyPlus co-simulation results}
After calibration, a comparison of co-simulation and solo EnergyPlus
simulations is made. Simulation time for the solo EnergyPlus simulation was 1 minute and 49 seconds 
compared to 28 minutes and 10 seconds for the co-simulation.

For cooling, a discrepancy can be seen between co-
simulation and solo EnergyPlus. Co-simulation decreases the predicted cooling energy by 15.5\%, as seen in Figure
\ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating}
illustrates the difference in predicted heating energy consumption across the
test year. A consistent offset exists across the time frame of days in
January, the peak of the heating season. A more varied discrepancy across the
heating months is noticed resulting an overall increase of heating prediction
of 6.5\% due to co-simulation. The exchange of long wave radiation for this
particular site is substantial due to the proximity of surrounding buildings.
These performance differences due to co-simulation are compared to a
theoretical single-zone case study in which there was a 15-30\% increase in
heating energy and a 4-11\% decrease in cooling energy \citep{Miller:2015vk}.
The results from this case study are less extreme on the heating side and more
on the cooling side than the theoretical case study.
